Spin canonical rings of log stacky curves

### 2015-07-08 curves-write-up/spin_cring.tex
moved o(D) definition

\begin{defn}
\label{defn:h0-stacky}
Let $\sx$ be a stacky curve with coarse space $X$.
If $D \in \di \sx$ is a Weil divisor, then we define

\[
	H^0(\sx, D) := H^0(X, \lfloor D \rfloor).
\]
\end{defn}

@@

\noindent
When the log spin curve is fixed, we usually use $R$ or $R_\halfcan$ to
represent $R(\sx, \Delta, \halfcan)$. We also often use $H^0(\sx, \sco(D))
:= H^0(\sx, D)$ and $h^0(\sx, \sco(D)) := \dim_k H^0(\sx, \sco(D)),$ where $\sco(D) = \{f \in k(X)^\times : \di f + D \geq 0 \}.$
If $R$ is a graded ring, then we let $(R)_d$ refer to the $d^\text{th}$
graded component of $R$.

>>>>

\begin{defn}
\label{defn:h0-stacky}
Recall the standard notation 
$$\sco(D) = \{f \in k(X)^\times : \di f + D \geq 0 \}.$$
Let $\sx$ be a stacky curve with coarse space $X$.
If $D \in \di \sx$ is a Weil divisor, then we define
\begin{align*}
	H^0(\sx, D) &:= H^0(X, \lfloor D \rfloor)\\
	H^0(\sx, \sco(D)) &:= H^0(\sx, D)\\
	h^0(\sx, \sco(D)) &:= \dim_k H^0(\sx, \sco(D))
\end{align*}
If $R$ is a graded ring, then we let $(R)_d$ refer to the $d^\text{th}$
graded component of $R$.

@@

\noindent
When the log spin curve is fixed, we usually use $R$ or $R_\halfcan$ to
represent $R(\sx, \Delta, \halfcan)$.
